%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Dragan Stojanović} \\ \vspace{1pt}
    \small +381642248984 $|$ \href{mailto:stojanovic.dragan.87@gmail.com}{\underline{stojanovic.dragan.87@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/stojanovic-dragan/}{\underline{linkedin.com/in/stojanovic-dragan/}} $|$
    \href{https://github.com/drakche/}{\underline{github.com/drakche}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Developer}{Oct. 2024 -- Present}
      {Constellation DOO}{Belgrade, Serbia}
      \resumeItemListStart
        \resumeItem{API development and maintenance of core back end systems on company projects.}
        \resumeItem{Primary focus is design and maintenance of core systems for a companies own product. Successfully optimized and streamlined several of the core services.}
        \resumeItem{\textit{Technologies}: NodeJS, Express, Mongo, PostgreSQL, RabbitMQ, React}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Senior Software Developer and Specialized UX/UI Consultant}{Jul. 2020 -- Oct. 2024}
      {Indata.dev}{New York, NY, USA}
      \resumeItemListStart
        \resumeItem{Full stack software development, rapid application prototyping and UX and UI optimization.}
        \resumeItem{I worked as an consultant for a US based company, and in the process delivered more than 15 projects and application prototypes. Primary focus of the projects was enabling clients to present and test out their ideas to investors and boards.}
         \resumeItem{\textit{Technologies}: Vue, NodeJS, Express, Mongo, SASS}
      \resumeItemListEnd

    \resumeSubheading
      {Tools Engineer}{Sept. 2019 -- July 2020}
      {Recogni Inc.}{San Jose, CA, USA}
      \resumeItemListStart
        \resumeItem{Development of internal debugging tools for data visualization. Designed and developed internal tools for a Silicone Valley startup with focus on data visualization for debugging autopilot chips.}
        \resumeItem{\textit{Technologies}: NodeJS, Express, Mongo, React, Python, Blender}
      \resumeItemListEnd
    \resumeSubheading
      {Full Stack Developer}{Mar. 2016 -- Sept. 2019}
      {Deploy Inc.} {Belgrade, Serbia}
      \resumeItemListStart
        \resumeItem{Web development of modern scalable applications. Focusing more on frontend development, and specifically UX/UI optimization and data visualization.}
        \resumeItem{Team leader. Managed a team of 4 for 2 years that successful migrated an older application to a completely new framework.}
        \resumeItem{\textit{Technologies}: NodeJS, Mongo, Vue, AngularJS, CSS3, React}
      \resumeItemListEnd
    \resumeSubheading
      {Senior Software Developer}{Dec. 2014 -- Mar. 2016}
      {Ondo Seti} {Belgrade, Serbia}
      \resumeItemListStart
        \resumeItem{Development of IoT control web applications. Delivered a high profile project for the Dubai Expo 2020.}
        \resumeItem{\textit{Technologies}: AngularJS, ASP.NET, SQLServer, Python, CouchDB}
      \resumeItemListEnd
    \resumeSubheading
      {Senior Software Developer}{Apr. 2014 -- Dec. 2014}
      {Circle Web Foundry DOO} {Pancevo, Serbia}
      \resumeItemListStart
        \resumeItem{Web development.}
        \resumeItem{\textit{Technologies}: AngularJS, Drupal}
      \resumeItemListEnd
    \resumeSubheading
      {Software Developer}{Apr. 2013 -- Apr. 2014}
      {Seavus DOO} {Belgrade, Serbia}
      \resumeItemListStart
        \resumeItem{Applicative development and fin-tech work.}
        \resumeItem{\textit{Technologies}: C\#, ASP.NET, JavaScript}
      \resumeItemListEnd
    \resumeSubheading
      {Junior Software Developer}{Aug. 2010 -- Mar. 2013}
      {S\&T Serbia} {Belgrade, Serbia}
      \resumeItemListStart
        \resumeItem{Application and web development. Most prominent work was on the Republic of Serbia eGovernment portal.}
        \resumeItem{\textit{Technologies}: C\#, ASP.NET,}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, Python, C\#, SQL (PostgreSQL, SQL Server, MySQL), HTML, CSS/LESS/SASS} \\
     \textbf{Frameworks}{: NodeJs, Express, Vue, Angular, React} \\
     \textbf{Developer Tools}{: Git, Docker, VS Code, Visual Studio, Yarn, NPM} \\
    }}
 \end{itemize}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Faculty of Organizational Sciences}{Univeristy of Belgrade}
      {B.SC in Organizational Sciences}{Oct. 2005 -- Apr. 2011}
  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
